Think deep for reef resilience

### 2025-08-09 paper/paper_draft.qmd
Add quantification of the influence of reef features on cluster assigns
Added quantification of cluster-level ~ reef factor affects (such as depth and connectivity) via a multinomial logistic regression (provided by Econometrics.jl pkg). This is an extension of binomial logistic regression.

This regression is performed individually for each GCM. Only ACCESS-ESM1-5 results are displayed in the paper.

Added table of model coefficients to the results section of paper but have not added these values into text or discussed values yet.

::: {#tbl-gcms}
| Global Climate Model source | ECS value (°C) | Interpreted relative severity | Results found in |
|-----------------------------|----------------|-------------------------------|------------------|
| EC-Earth3-Veg               | 4.31           | High                          | **insert repo citation**    |
| ACCESS-CM2                  | 4.72           | High                          | **insert repo citation**    |
| ACCESS-ESM1-5               | 3.87           | Intermediate                  | Main text        |
| GFDL-CM4                    | 2.9            | Low                           | **insert repo citation**    |
| NorESM2-MM                  | 2.5            | Low                           | **insert repo citation**    |

@@

**[TI and BG to flesh out]**

@@

>>>>

::: {#tbl-gcms}
| Global Climate Model source | ECS value (°C) | Interpreted relative severity | Results found in |
|-------------------------|--------------------|---------------------------|--------------------|
| EC-Earth3-Veg | 4.31 | High | **insert repo citation** |
| ACCESS-CM2 | 4.72 | High | **insert repo citation** |
| ACCESS-ESM1-5 | 3.87 | Intermediate | Main text |
| GFDL-CM4 | 2.9 | Low | **insert repo citation** |
| NorESM2-MM | 2.5 | Low | **insert repo citation** |

@@

**\[TI and BG to flesh out\]**

@@

```{julia}
#| echo: false
#| warning: false
#| message: false
#| results: asis
#| label: tbl-access-esm1-5-bioregion-regression
#| tbl-cap: Multinomial logistic regression coefficients for the statistical model containing median reef depth, natural-log total connectivity strength, natural-log source-to-sink ratio and ACCESS-ESM1-5 mean timeseries DHW value as predictor variables. ACCESS-ESM1-5 bioregion scale reef cluster assignment is the response variable with three levels, 'low' (regression reference level), 'medium' and 'high'.

using PrettyTables, Markdown
cd("../src")

include("../src/common.jl")

cluster_regression = CSV.read(joinpath(output_path, "cluster_regression_outputs/ACCESS-ESM1-5_bioregion_cluster_regression_coefficients.csv"), DataFrame)
cluster_regression.Name = replace.(cluster_regression.Name, ["ACCESS-ESM1-5_bioregion_cluster_cats: " => "Cluster "])

for name in names(cluster_regression)
    if isa(cluster_regression[:, name], Vector{Float64})
        cluster_regression[:, name] = round.(cluster_regression[:, name]; sigdigits=2)
    end
end

header = ["Response level ~ Term", "β estimate", "SE", "t-value", "Pr > |t|", "2.5%", "97.5%"]
pretty_table(io, cluster_regression, backend = Val(:markdown), header = header)
